Are people really struggling to find a job?

### 2024-03-26 paper/paper.qmd
updated paper and llm

@@

@@

@@

>>>>

The following formula was used to calculate the net percentage change in the unemployment rate:

$$
\text{Net Percentage Change} = \left( \frac{\text{Value at End Period} - \text{Value at Start Period}}{\text{Value at Start Period}} \right) \times 100\%
$$

@@

We then used the following formula to calculate the overall percentage change between years:

$$
\text{Overall Percentage Change} = \left( \frac{\text{Sum of Rates in X Year} - \text{Sum of Rates in Y Year}}{\text{Sum of Rates in Y Year}} \right) \times 100\%
$$

The overall percentage change for the youth unemployment rate is $\approx 0.92 \%$ increase between 2019 and 2023 and $\approx 10.45 \%$ increase between 2022 and 2023.

@@

Again using the same formula as before, the overall percentage change for the adult unemployment rate is $\approx 0.89 \%$ increase between 2019 and 2023 and $\approx 9.98 \%$ increase between 2022 and 2023.

@@

The overall percentage change for the senior unemployment rate is $\approx 13.54 \%$ decrease between 2019 and 2023 and $\approx 6.11 \%$ decrease between 2022 and 2023.
